EBCM Directory Roadmap

### 2023-05-19 example/EBCM/roadmap.tex
moved cell merged examples into their own space

\title{EBCM Directory Roadmap}
\author{
    D. T. Graves    \footnotemark[1]
        }
\date{May 7, 2023 ce.}
\maketitle

@@

This tests the communications infrastructure for {\tt
Chombo4/src/EBCM}, the bits of Chombo that handle calculations
within the context merged and
unmerged cut cell geometries.   The associated document is complete
but minimal.

>>>>

\title{EBCM Directory Roadmap}
\author{ D. T. Graves }
\date{May 7, 2023 c.e.}
\maketitle

@@

This tests the communications infrastructure for {\tt
Chombo4/src/EBCM}, the bits of Chombo that handle calculations
within the context of  cut cell geometries where merger is an option.
The associated document is complete but minimal.
